Tree size, microhabitat, and hydraulic traits shape drought responses in a temperate broadleaf forest

### 2019-09-19 manuscript/climate_sensitivity_draft.Rmd
worked on results

@@

Overall, our analysis confirmed the tendency for larger-diameter trees to show greater reductions in growth during drought [@bennett_larger_2015] (*H1.0*), although there was no signficant effect for 1977 or 1999 individually (Tables 1, 4). The same held true for height as a univariate predictor (*H1.1*; Tables 1, 4). When combined with other predictor variariables in our multivariate models, the top models usually included an effect of height, and its coefficient was consistently negative, as predicted (Tables 1, 5). We note that a non-signficant positive correlation between $H$ and $R$ for 1999 became negative in the context of the multivariate models, again supporting *H1.1* (Table 1).
H1.0, H1.1, H1.2, H1.3
DBH, height, crown position, and TWI

@@

**Results for second main question: how do species' traits - alone and in interaction with tree size - influence drought response? **
H2.1, H2.2, H2.3
Hydraulic traits alone, traits with height

>>>>

Overall, our analysis confirmed the tendency for larger-diameter trees to show greater reductions in growth during drought [@bennett_larger_2015] (*H1.0*), although there was no signficant effect for 1977 or 1999 individually (Tables 1, 4). The same held true for $ln[H]$ as a univariate predictor (*H1.1*; Tables 1, 4). When combined with other predictor variariables in our multivariate models, the top models usually included an effect of $ln[H]$, and its coefficient was consistently negative, as predicted (Tables 1, 5). We note that a non-signficant positive correlation between $ln[H]$ and $R$ for 1999 became negative in the context of the multivariate models, again supporting *H1.1* (Table 1).

In the non-drought years for which we have vertical profiles in climate data (**YEARS**), taller trees--or those in dominant crown positions-- were generally exposed to higher evaporative demand during the peak growing season months (May-August; Fig. 2). Specifically, [**add content on vertical profiles of climate variables**]

@@

Crown position was generally correlated with $H$, but with substantial variation (Fig. 2e). Crown position was a much poorer predictor of $R$ than was $H$ (Table 4), lending little overall support to *H1.2* (Table 1). When considered alone, $CP$ had a significant influence only in the 1977 drought, during which trees with dominant $CP$ had the lowest $R$. When considered in conjunction with $H$, $CP$ came out as a significant predictor only for the 1999 drought, during which suppressed trees had the lowest $R$. Crown position was included in **roughly half** of the top models, with mixed results as to how $R$ varied with $CP$ (Table 5). Most commonly in these multivariate models, as in the univariate models (Table 4), the resistance of dominant trees was less than that of co-dominant trees but higher that of suppressed trees. Thus, $CP$ was sometimes a useful predictor of $R$, but overall had a weak effect relative to that of $H$.

Resistance was negatively correlated with $ln[TWI]$ (Tables 4-5), negating the idea that trees in moist microsites would suffer less during drought. Nevertheless, we tested for a negative $ln[H] *ln[TWI]$ interaction (*H1.3*), which could indicate that smaller trees (with smaller rooting volume) have a greater tendency to suffer more in drier microenvironments with greater depth to the water table. *H1.3* was rejected; the $ln[H] *ln[TWI]$ interaction was never signficant and had a consistently positive coefficient (Table 4).

@@

*Species' traits and drought resistance*
H2.1, H2.2, H2.3
Hydraulic traits alone, traits with height
